### 2021-09-22 paper/manuscript.Rmd
Results for predictive performance R2 and .rtf document containing relevant images

 *$y_{i}$ = θ + $ϵ_{i}$ * 						(1)

@@

 *$W_{i}$=  1/($σ^2_{i}$)*						  (2)

@@

 *$y_{i}$ = $θ_{i}$+$ϵ_{i}$* 						(3)

@@

 *$θ_{i}$= μ + $ζ_{i}$*						(4)

@@

#Results
There were 20 cases out of 388800 that had missing values for the RMA algorithm. Closer inspection showed that both the cubic and exponential model each contributed 10 times to the missing values and only when 2, 3 or 6 moderators were taken up in the model. However, since this makes up 0.005% of the data, the missing values were chosen to be omitted from further analysis.

*Predictive performance*
Because the densities for the R2 values were either bimodal or skewed, it was chosen to use the median $R^{2}$ as the metric for predictive performance, rather than the mean. The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation. It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $Med_{hs}$ = 0.51, MAD = 0.36; $Med_{Lasso}$ = 0.50, MAD = 0.37; $Med_{RMA}$ = 0.50, MAD = 0.37. The random forest algorithm performed worst $Med_{rf}$ = 0.35, MAD = 0.38.

To determine the effect of the design factors on predictive performance of all algorithms, four separate ANOVA’s was performed. The $η^{2}$ per condition per algorithm can be found in table 1.

Not too surprisingly, It was found that the true effect size *β* had the largest effect on the predictive $R^{2}$ for all algorithms. As *β* increased, the performance of all algorithms increased as well. However, *β* did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. The image of the interaction is shown in image 1. The major difference seems to be that for all models, except the linear, the increase of *R2* slows for every higher value for *β*. The steepest increase for the linear model is when *β* increases from 0.2 to 0.4. Also noteworthy is that the two-way interaction model seems to stagnate as the effect size goes up to 0.4 onwards, while the other models do keep increasing, although not as severely. There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while the random forest algorithm performed worst.

The second largest marginal effect was that of the estimated model. All algorithms performed best under the 2-way interaction model, followed by a similar performance on the cubic and exponential models. The linear model predicted worst performance for all algorithms. Horseshoe and Lasso performed best under all models, followed closely by RMA and lastly the random forest. Image 2 shows the relationship.

There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [α], especially for the Pema algorithms. Again, the Horseshoe and Lasso algorithms performed best, followed by RMA and MetaForest in all conditions. Most obvious to note is that under all model, except the linear model, the algorithms benefitted when the $R^{2}$ was estimated on more skewed data. The two-way interaction model performs best under all levels of *α*, but is getting caught up by the exponential and cubic model as *α* increases. Image 3 shows the relationship.

The true residual heterogeneity $τ^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $τ^{2}$ increases, $R^{2}$ decreased. The effect was slightly bigger for the Pema algorithms than for the other two. Still, both Horseshoe and Lasso performed best, followed by RMA and MetaForest. Image 4 shows the relationship.

The mean sample size per study [n] also had a moderate effect, again namely for the Pema algorithms. For all algorithms the effect of *n* was positively linearly related to $R^{2}$ with the Pema algorithms performing best for all levels of *n*. Image 5 shows the relationship.

@@

Finally, the number of moderators did not have a big effect for the Pema algorithms, $η^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $η^{2}$ = 0.05. This relationship is generally negative with more moderators meaning worse performance, although a slight increase can be observed as the number of moderators increase from 6 to 7. The image and $η^{2}$ values indicate that the Pema algorithms seem more robust against number of moderators than RMA and MetaForest.

>>>>

 $y_{i}$ = θ + $ϵ_{i}$						(1)

@@

 $W_{i}$=  1/($σ^2_{i}$)						  (2)

@@

 $y_{i}$ = $θ_{i}$+$ϵ_{i}$ 						(3)

@@

 $θ_{i}$= μ + $ζ_{i}$						(4)

@@

#Results
There were 20 cases out of 388800 that had missing values on all metrics for the RMA algorithm. Closer inspection showed that both the cubic and exponential model each contributed 10 times to the missing values and only when 2, 3 or 6 moderators were taken up in the model. However, since this makes up 0.005% of the data, the missing values were chosen to be omitted from further analysis.

*Predictive performance*
Because the densities for the $R^{2}$ values were either bimodal or skewed, it was chosen to use the median $R^{2}$ as the metric for predictive performance, rather than the mean. The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation. It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $Med_{hs}$ = 0.51, MAD = 0.36; $Med_{Lasso}$ = 0.50, MAD = 0.37; $Med_{RMA}$ = 0.50, MAD = 0.37. The random forest algorithm performed worst $Med_{rf}$ = 0.35, MAD = 0.38.

To determine the effect of the design factors on predictive performance of all algorithms, four separate ANOVA’s were performed. The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 1.

Not too surprisingly, It was found that the true effect size $β$ had the largest effect on the predictive $R^{2}$ for all algorithms. As $β$ increased, the performance of all algorithms increased as well. However, $β$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. The image of the interaction is shown in image 1. For the exponential and two-way interaction model, the increase of $R^{2}$ slows for every higher value for $β$. The cubic model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $β$ increases from 0.2 to 0.4. Also noteworthy is that the two-way interaction model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing. There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while the random forest algorithm performed worst.

The second largest marginal effect was that of the estimated model. It seemed that all algorithms performed best under the two-way interaction model, followed by a similar performance on the cubic and exponential models. All algorithms seemed to perform worst for the linear model. There again is little difference in performance between the Pema algorithms and RMA, altough the random forest performs worst. Image 2 shows the relationship.

There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [$α$], especially for the Pema algorithms. Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions. Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse when the model is cubic and $α$ goes from 5 to 10. The two-way interaction model performs best overall, but is getting caught up by the exponential and cubic model as $α$ increases. Image 3 shows the relationship.

The true residual heterogeneity $τ^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $τ^{2}$ increases, $R^{2}$ decreased. Image 4 shows the relationship.

The mean sample size per study [$n$] also had a moderate effect. For all algorithms the effect of $n$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worse. Image 5 shows the relationship.

@@

Finally, the number of moderators did not have a big effect for the Pema algorithms, $η^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $η^{2}$ = 0.05. This relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except Metaforest. This increase in performance for Metaforest appears when the number of moderators go from 3 to 4. Image 7 and $η^{2}$ values indicate that the Pema algorithms seem more robust against number of moderators than RMA and MetaForest.

#Estimating residual heterogeneity ($τ^{2}$)
The ability of the algorithms to correctly estimate $τ^{2}$ was operationalized by subtracting the true value for $τ^{2}$ from the $τ^{2}$ estimated by the algorithms. Again, the median and MAD were used as metrics for performance. The RMA algorithm showed the best results, $Med_{rma}$ = 0.02, MAD = 0.06, followed by the Metaforest algorithm $Med_{mf}$ = 0.09, MAD = 0.13. The Pema algorithms performed worst $Med_{lasso}$ = 0.23, MAD = 0.18; $Med_{hs}$ = 0.23, MAD = 0.17. The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $τ^{2}$ than underestimate it.

To determine the effect of the design factors on estimated $τ^{2}$ of all algorithms, four separate ANOVA’s were performed. The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 2.
